---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GDPuc

<!-- badges: start -->

[![CRAN status](https://www.r-pkg.org/badges/version/GDPuc)](https://CRAN.R-project.org/package=GDPuc) [![check](https://github.com/pik-piam/GDPuc/actions/workflows/check.yaml/badge.svg)](https://github.com/pik-piam/GDPuc/actions/workflows/check.yaml) 
[![codecov](https://codecov.io/gh/pik-piam/GDPuc/branch/main/graph/badge.svg?token=3GHXFQXARX)](https://app.codecov.io/gh/pik-piam/GDPuc) 
![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)
<!-- badges: end -->

GDPuc (a.k.a. the GDP unit-converter) provides a simple function to convert GDP time-series data from one unit to another.

**To note:** The default conversion parameters are from the World Bank's World Development Indicators (WDI) database (see [link](https://databank.worldbank.org/source/world-development-indicators)). The current parameters are from **April 30th 2024**, with the next update planned for April 2026.

## Installation

```{r, eval = FALSE}
# Install from CRAN
install.packages("GDPuc")

# Or the development version from GitHub
remotes::install_github("pik-piam/GDPuc")
```

## Usage

Load the package.

```{r eval=FALSE}
library(GDPuc)
```

The main function of the package is `convertGDP`.

```{r usage1, eval=FALSE}
convertGDP(
  gdp = my_gdp,
  unit_in = "constant 2005 LCU",
  unit_out = "constant 2017 Int$PPP"
)
```

Here, the `gdp` argument takes a tibble or a data-frame that contains, at least:

-   a column with iso3c country codes, (ideally named "iso3c"),
-   a column with the year, (ideally named "year"),
-   a column named "value", with the gdp data.

The `unit_in` and `unit_out` arguments specify the incoming and outgoing GDP units. All common GDP units are supported, i.e.:

-   current LCU
-   current US$MER
-   current Int$PPP
-   constant YYYY LCU
-   constant YYYY US$MER
-   constant YYYY Int$PPP

Here "YYYY" is a placeholder for a year, e.g. "2010" or "2015", and "LCU" stands for Local Currency Unit.

For a quick conversion of a single value use `convertSingle`.

```{r usage2, eval=FALSE}
convertSingle(
  x = 100,
  iso3c = "FRA",
  year = 2000,
  unit_in = "current LCU",
  unit_out = "constant 2017 Int$PPP"
)
```


## Example

```{r example1}
library(GDPuc)

my_gdp <- tibble::tibble(
  iso3c = "USA",
  year = 2010:2014,
  value = 100:104
)
print(my_gdp)

convertGDP(
  gdp = my_gdp,
  unit_in = "constant 2005 LCU",
  unit_out = "constant 2017 Int$PPP"
)

convertSingle(
  x = 100,
  iso3c = "USA",
  year = 2010,
  unit_in = "current LCU",
  unit_out = "constant 2017 Int$PPP"
)

# When converting between constant currencies, the year of the GDP value is not important,
# and can be left out.
convertSingle(
  x = 100,
  iso3c = "USA",
  unit_in = "constant 2005 LCU",
  unit_out = "constant 2017 Int$PPP"
)
```

## Further Options

`convertGDP` has other arguments that allow you to:

-   choose conversion factors (see ["Choosing conversion factors"](https://pik-piam.github.io/GDPuc/articles/source.html))

-   print out information on the conversion process and/or return the conversion factors used (see ["Getting information on the conversion process"](https://pik-piam.github.io/GDPuc/articles/verbose.html))

-   handle missing conversion factors (see ["Handling missing conversion factors"](https://pik-piam.github.io/GDPuc/articles/handle_NAs.html))

-   convert regional GDP data (see ["Converting regional GDP data"](https://pik-piam.github.io/GDPuc/articles/with_regions.html))
