---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GDPuc

<!-- badges: start -->

[![R-CMD-check](https://github.com/johanneskoch94/GDPuc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/johanneskoch94/GDPuc/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

GDPuc (a.k.a. GDP unit-conversion) provides a single function to convert GDP time-series data from one unit to another. All common GDP units are supported.

## Installation

Since this is still a private repository, you'll need a [github personal acces token](https://docs.github.com/en/github/authenticating-to-github/creating-a-personal-access-token) with "repo" scope. Once you've created this token, you can use it to install GDPuc directly from github.

Open a R session on your machine, either in Rstudio (recommended), or from the command line with the `R` command.

```{r, eval = FALSE}
# Make sure devtools is installed:
install.packages("devtools")

# Install GDPuc from github:
devtools::install_github(
  repo = "johanneskoch94/GDPuc",
  auth_token = "<<your personal github acces token goes here>>"
)
```

## Usage

The function `convertGDP` takes a tibble that contains at least:

-   a column with iso3c country codes, (ideally named "iso3c")
-   a column with the year, (ideally named "year")
-   a column named "value", with the gdp data 

and converts the "value" column from the unit specified by the `unit_in` argument, into that specified by `unit_out`. 
It uses GDP deflators, MERs and PPPs from the database specified by the `source` argument (defaults to the world bank's Feb. 2021 WDI).  

Allowed in- and out-units are:

-   "current LCU"
-   "current US$MER"
-   "current Int$PPP"
-   "constant YYYY LCU"
-   "constant YYYY US$MER"
-   "constant YYYY Int$PPP"  

where "YYYY" should be replaced by a year, e.g. "2010" or "2015".

```{r usage, eval=FALSE}
# Load package into R-session
library(GDPuc)

# Convert gdp
convertGDP(
  gdp = gdp, 
  unit_in = "constant 2005 LCU", 
  unit_out = "constant 2017 Int$PPP"
)
```

## Example

```{r example}
library(GDPuc)

gdp <- tibble::tibble(iso3c = "USA", year = 2010:2020, value = 100:110)
print(gdp)

convertGDP(gdp, "constant 2005 LCU", "constant 2017 Int$PPP")
```
