---
title: "Using a custom set of conversion factors"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using a custom set of conversion factors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(GDPuc)
```

## The 'source' argument

## Default conversion factors

```{r}
print_source_info("wb_wdi")
```


Use the `source` argument to control the source of the underlying conversion factors (GDP deflators, MERs and PPPs). There are two source options shipped with the package, `wb_wdi` and `wb_wdi_linked` (with `wb_wdi` set as the default), but custom sources are possible. A custom source can be any tibble with columns:

-   "iso3c" (character),
-   "year" (numeric),
-   "GDP deflator" (numeric),
-   "MER (LCU per US$)" (numeric),
-   "PPP conversion factor, GDP (LCU per international $)" (numeric)


```{r}


gdp <- tibble::tibble(
  iso3c = "USA", 
  year = 2010:2014, 
  value = 100:104
)
print(gdp)

convertGDP(
  gdp = gdp, 
  unit_in = "constant 2005 LCU", 
  unit_out = "constant 2017 Int$PPP"
)
```
